---
title: "7.9.6 polynomial regression with cv"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. data processing
```{R}
library(ISLR)
library(boot)
summary(Wage)
head(Wage)
attach(Wage)
```

(a) Perform polynomial regression to predict wage using age.Use cross-validation to select the optimal degree d for the polynomial. What degree was chosen, and how does this compare to the results of hypothesis testing using ANOVA? Make a plot of the resulting polynomial fit to the data.

2.select the optimal degree d
```{R}
set.seed(1)
cv.error=rep(NA,10)
for (i in 1:10){
  pl.fit=glm(wage~poly(age,i))
  cv.error[i]=cv.glm(Wage,pl.fit, K=10)$delta
}
plot(cv.error,  type="b")
```

3. ANOVA
```{r}
glm.fit1=glm(wage~age)
glm.fit2=glm(wage~poly(age,3))
glm.fit3=glm(wage~poly(age,4))
glm.fit4=glm(wage~poly(age,5))
anova(glm.fit1,glm.fit2,glm.fit3,glm.fit4,test="F")
```

(b) Fit a step function to predict wage using age, and perform crossvalidation to choose the optimal number of cuts. Make a plot of the fit obtained.
4.Cross validation to choose optimal number of cuts
```{R}
set.seed(1)
cv.error1=rep(NA,19)
for (i in 2:20){
  Wage$age.cut = cut(Wage$age,i)
  step.fit=glm(wage~age.cut, data=Wage)
  cv.error1[i-1]=cv.glm(Wage,step.fit, K=10)$delta[1]
}
plot(cv.error1,  type="b")
# optimal number=7+1
```

5. step function with optimal number
```{R}
agelims=range(age)
age.grid=seq(from=agelims[1],to=agelims[2])

step.fit1=glm(wage~cut(age,8))
pred=predict(step.fit1,newdata=list(age=age.grid), se=T)
se.bands=cbind(pred$fit+2*pred$se.fit,pred$fit-2*pred$se.fit)
plot(age,wage,cex=.5,col="darkgrey")
lines(age.grid, pred$fit, col="orange", lwd=2)
matlines(age.grid, se.bands, col="blue", lwd=2, lty=3)
```